Precise Asymptotics of Learning from Different Data Sources in High-dimensional Regression

### 2021-06-28 revision_journal/setup.tex
add references

\paragraph{Transfer learning.}
There is a large body of classical and recent works on multi-task learning.
We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting}.
For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
However, their results only apply to sample size regimes at least logarithmic factors of dimension.
\todo{a list of relevant papers}
\begin{itemize}
	\item \citet{lei2021nearoptimal}
	\item \citet{kalan2020minimax}
	\item \citet{cao2019learning}
\end{itemize}
\textit{Other related works.} Distributed learning \cite{dobriban2018high}.
\citet{chen2021weighted}

\paragraph{Random matrix theory.}
\todo{write a paragraph regarding applications of RMT to modern machine learning.}

Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
\HZ{can you please add a discussion of the related work from RMT?}

>>>>

\paragraph{Transfer learning.}
There is a large body of classical and recent works on multi-task learning.
We focus our discussion on theoretical results and refer interested readers to several excellent surveys for general references \cite{PY09,ZY17,V20}.
The early work of \cite{B00,BS03,M06} studied multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
An influential paper by \cite{BBCK10} provides uniform convergence bounds that combine multiple datasets in certain settings.
One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, see e.g. \cite{B00,MPR16}.
Moreover, these techniques do not apply to the high-dimensional setting because the results usually require a sample size of at least $p \log p$.
The problem we study here is also related to high-dimensional prediction in transfer learning \cite{li2020transfer,bastani2020predicting}.
For example, \cite{li2020transfer} provide minimax-optimal rates to predict a target regression task given multiple sparse regression tasks.
\citet{tian2021transfer}
One closely related work is \cite{WZR20}, which studied hard parameter sharing for two linear regression tasks.
However, their results only apply to sample size regimes at least logarithmic factors of dimension.
\todo{a list of relevant papers}
\begin{itemize}
	\item \citet{lei2021nearoptimal}
	\item \citet{kalan2020minimax}
	\item \citet{cao2019learning}
	\item \citet{hanneke2020value,hanneke2020no}
\end{itemize}
\textit{Other related works.} Distributed learning \cite{dobriban2018high}.
\citet{chen2021weighted}

\paragraph{Random matrix theory.}
\todo{write a paragraph regarding applications of RMT to modern machine learning.}
\begin{itemize}
	\item \citet{hastie2019surprises}
	\item \citet{bartlett2020benign}
	\item \citet{liang2020just}
	\item \citet{montanari2019generalization}, \citet{liang2020precise}
\end{itemize}

Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, a recent development in the random matrix theory literature.
In the single-task case, \cite{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
\cite{Anisotropic} later extended this result to arbitrary covariance matrices.
%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
These techniques provide almost sharp convergence rates to the asymptotic limit compared to other methods such as free probability \cite{nica2006lectures}.
To the best of our knowledge, we are not aware of any previous results in the multi-task case, even for two tasks (with arbitrary covariate shifts).
%\HZ{can you please add a discussion of the related work from RMT?}
